Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-19 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
working on case study

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1.
The buffer function and clip function are from library \emph{Clipper} 
of \citet{Johnson2014}.
An evaluation of Clipper can be found in \citet{Palfrader2015}.
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
We tested our method on a dataset from French Mapping Agency (IGN).
The dataset represents four towns (communes in French), i.e., Aussevielle, 
Denguin,  Poey-de-Lescar, and Siros, in the 
Pyr\'en\'ees-Atlantiques department, south-western France.
The scale of the dataset is $1:15{,}000$.
There are $2{,}590$ buildings (see \fig\ref{fig:Data}), 
which has $19{,}255$ edges in total.
Our goal scale is $1:50{,}000$.

\begin{figure*}[tb]
	\centering
	\includegraphics{Data}
	\caption{data.}
	\label{fig:Data}
\end{figure*}

\todo[inline]{comparison of simplification between Douglas--Peucker and 
	Imai--Iri}

>>>>

\section{Case Study}
\label{sec:CaseStudy}
We have implemented our method based on
C\# (Microsoft Visual Studio 2015) and ArcObjects SDK 10.4.1.
The offsetting function and clipping function are from library \textsc{Clipper} 
of \citet{Johnson2014}.
The offsetting function realizes 
our operations of buffering, dilating, eroding, and merging.
An evaluation of \textsc{Clipper} can be found in \citet{Palfrader2015}.
We ran our case study under 64-bit 
Windows 7 on a 3.3 GHz dual core CPU with 8 GB RAM.
We measured processing time by the built-in C\# class 
\emph{Stopwatch}.
\fig\ref{fig:Data} shows our testing data, 
which is from the French Mapping Agency (IGN).
The data represents the buildings of four towns (communes in French), 
i.e., Aussevielle, Denguin,  Poey-de-Lescar, and Siros, 
in the Pyr\'en\'ees-Atlantiques department, south-western France.

We set our goal scale at $1:50{,}000$ and $d_\mathrm{G}=25\,\mathrm{m}$
so that we can compare our result with the exiting data.
Also, this setting makes \eq\ref{eq:S_g} hold, 
where $M_\mathrm{g}=50{,}000$, $d_\mathrm{G}=25\,\mathrm{m}$, 
and $l=0.3\,\mathrm{mm}$.
In \eq\ref{eq:d_Dtmin}, the first part is always smaller than the second part 
according to our settings.
As a result $\dtrm{D}=t\cdot 35\,\mathrm{m}$, 
where $\dtrm{E}=t\cdot 7.5\,\mathrm{m}$ 
according to \eq\ref{eq:d_Et} and $\alpha=1.5$.

Our program took $93.6\,\mathrm{s}$ 
to compute the goal shapes of the built-up areas.
\fig\ref{fig:GoalShape} shows the bridged buildings and the goal shapes.
In \fig\ref{fig:GoalShape}b,
the $56$ built-up areas have $2{,}095$ edges before line simplification.
Using the Imai--Iri algorithm, we have $1{,}102$ edges left.
In comparison, there are $1{,}597$ edges left if we simplify using
the Douglas--Peucker algorithm.

\begin{figure}[tb]
	\centering
	\includegraphics{Data}
	\caption{Data.
		There are $2{,}590$ buildings, 
		which have $19{,}255$ edges in total.}
	\label{fig:Data}
\end{figure}

\begin{figure*}[tb]
	\centering
	\includegraphics{GoalShape}
	\caption{Bridged original buildings 
		and goal shapes of the built-up areas (without removing small holes), 
		at scale $1:50{,}000$.
		There are $56$ built-up areas, which have $1{,}102$ edges in total.
	}
	\label{fig:GoalShape}
\end{figure*}

\begin{figure*}[tb]
	\centering
	\includegraphics{ExperimentalComparison}
	\caption{.
	}
	\label{fig:ExperimentalComparison}
\end{figure*}
